---
title: "Disturbance_contrasts"
author: "Jo"
date: "31/01/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("fix_chl.R")
source("Graphing_Set_Up.R")
library(lme4)
library(tidyquant)
library(emmeans)
library(gridExtra)
library(sjstats)
library(stringr)
```


Remove treatments with ceriodaphnia since they didn't survive
```{r}
dat <- newdat %>% filter(! treatment %in% c(5,6,9,10,13,14))
dim(dat)
```

make a columns for disturbed/undisturbed and both/none/cladoceran/snail

```{r}
dat$disturb <- "X"
  
for (i in 1:nrow(dat)){
  if (dat$treatment[i] ==2| dat$treatment[i] ==4| dat$treatment[i] ==8|
      dat$treatment[i] ==12){
    dat$disturb[i] <- "y"
  } else if (dat$treatment[i] ==1|dat$treatment[i] ==3|dat$treatment[i] ==7|dat$treatment[i] ==11){
    dat$disturb[i] <- "n"
  }}

dat$animal <- "X"

for (i in 1:nrow(dat)){
  if (dat$treatment[i] ==3| dat$treatment[i] ==4){
    dat$animal[i] <- "daphnia"
  } else if (dat$treatment[i] ==7|dat$treatment[i] ==8){
    dat$animal[i] <- "snail"
  } else if (dat$treatment[i] ==11|dat$treatment[i] ==12){
    dat$animal[i] <- "both"}
  else if (dat$treatment[i] ==1|dat$treatment[i] ==2){
    dat$animal[i] <- "none"}
}


```



```{r, dates}

## need dummy date variable for tq_mutate to work.... and for random effect of experimental block

Date <- paste(dat$Month, dat$Day,dat$Year, sep = "-")


betterDates <- as.Date(Date,
  format = "%B-%d-%Y")

dates <- data.frame(Dates1 = Date,
                    Dates2 = betterDates)

p <- dates %>% filter(is.na(Dates2))
which(is.na(dates$Dates2))
dates[c(390,400,409,418,421,440),2] <- "2019-03-02"
dates[419,2] <- "2019-01-31"
dates[498,2] <- "2019-02-03"
dates[(which(is.na(dates$Dates2))), 2] <- "2019-03-01"

dat$Date <- dates$Dates2

## add blocking variable
block <- dat %>% filter(ExptDay == 1) %>% dplyr::select(Date, ExptDay, TankNum)
block$block <- NA
for (i in 1:nrow(block)){
  if (block$Date[i] == "2019-01-21" ) {
    block$block[i] <- "A"
  } else if (block$Date[i] == "2019-02-21" ) {
     block$block[i] <- "B"
  } else if (block$Date[i] == "2019-01-22" ) {
     block$block[i] <- "C"
  } else if (block$Date[i] == "2019-01-25" ) {
     block$block[i] <- "D"
  } else if (block$Date[i] == "2019-03-02" ) {
     block$block[i] <- "E"
  } else if (block$Date[i] == "2019-01-28" ) {
     block$block[i] <- "F"  
  } else if (block$Date[i] == "2019-01-30" ) {
     block$block[i] <- "G"  
  } else if (block$Date[i] == "2019-03-01" ) {
     block$block[i] <- "H"   
  } else if (block$Date[i] == "2019-02-02" ) {
     block$block[i] <- "I" 
  } else if (block$Date[i] == "2019-02-04" ) {
     block$block[i] <- "J"  
  } else if (block$Date[i] == "2019-02-05" ) {
     block$block[i] <- "K"   
  } 
}

block <- block %>% dplyr::select(TankNum, block)
dat <- left_join(dat,block, by = "TankNum")
dim(dat)
dat$disturb <- factor(dat$disturb,levels = c("y", "n"))
```

Subset final time point for Nh4 and final 4 days for Chl
```{r final time point}
fday <- dat %>% filter(ExptDay == 40)
l <- as.numeric(unique(fday$TankNum))
fday1 <- dat %>% filter(ExptDay == 39) %>% filter(TankNum !=20 & TankNum !=21 & TankNum !=22 & TankNum != 23 &
                                                  TankNum !=24 & TankNum !=25 & TankNum !=26 & TankNum != 27 & 
                                                  TankNum !=28 & TankNum !=29 & TankNum !=30 & TankNum != 31 & 
                                                  TankNum !=32 & TankNum !=33 & TankNum !=34 & TankNum != 35 & 
                                                  TankNum !=36 & TankNum !=37 & TankNum !=38 & TankNum != 39 & 
                                                  TankNum !=40 & TankNum !=83 & TankNum !=84 & TankNum != 85 & 
                                                  TankNum !=86 & TankNum !=87 & TankNum !=88 & TankNum != 89 & 
                                                  TankNum !=90 & TankNum !=91 & TankNum !=92 & TankNum != 93 &
                                                  TankNum !=94 & TankNum !=95 & TankNum !=96 & TankNum != 97 & 
                                                  TankNum !=98 & TankNum !=99 & TankNum !=100& TankNum != 101 & 
                                                  TankNum != 102 & TankNum != 103 & TankNum != 104 & TankNum != 105 & 
                                                  TankNum != 106 & TankNum != 107) 
finday <- rbind(fday, fday1)
dim(finday)


endday <- dat %>% filter(ExptDay == 40 | ExptDay == 39 | ExptDay == 38 | ExptDay == 37)
endday1 <- dat %>% filter(ExptDay == 36) %>% filter(TankNum !=20 & TankNum !=21 & TankNum !=22 & TankNum != 23 &
                                                  TankNum !=24 & TankNum !=25 & TankNum !=26 & TankNum != 27 & 
                                                  TankNum !=28 & TankNum !=29 & TankNum !=30 & TankNum != 31 & 
                                                  TankNum !=32 & TankNum !=33 & TankNum !=34 & TankNum != 35 & 
                                                  TankNum !=36 & TankNum !=37 & TankNum !=38 & TankNum != 39 & 
                                                  TankNum !=40 & TankNum !=83 & TankNum !=84 & TankNum != 85 & 
                                                  TankNum !=86 & TankNum !=87 & TankNum !=88 & TankNum != 89 & 
                                                  TankNum !=90 & TankNum !=91 & TankNum !=92 & TankNum != 93 &
                                                  TankNum !=94 & TankNum !=95 & TankNum !=96 & TankNum != 97 & 
                                                  TankNum !=98 & TankNum !=99 & TankNum !=100& TankNum != 101 & 
                                                  TankNum != 102 & TankNum != 103 & TankNum != 104 & TankNum != 105 & 
                                                  TankNum != 106 & TankNum != 107)

end <- rbind(endday, endday1)


```

Final day model
```{r}
##remove 2 NA values
finmod00 <- lmer(log(adj_chl) ~ -1 + animal*disturb + (1|block), data =  end[end$adj_chl > 0, ])
plot(resid(finmod00))
qqnorm(resid(finmod00))

```

Contrasts of interest
```{r}
chlfin <- contrast(regrid(emmeans(finmod00, ~animal*disturb)), interaction = c("pairwise"), by = NULL)


##for graphing
chlfin1 <- emmeans(finmod00, ~animal*disturb)
chlfin2 <- data.frame(confint(pairs(chlfin1, simple = "disturb")))

```

Find maximum three day window 
```{r chl max}
dat <- dat %>% filter(!is.na(adj_chl))
#dat_dist <- dat %>% filter(ExptDay >= ExptDay[which(dat$Disturbed=="y")]) ## only days after disturbance, this doesn't work for non-disturbed treatments- obviously
dat_dist <- dat %>% filter(ExptDay > 19)

chl_rollmean <- dat_dist %>% group_by(treatment) %>%
    tq_mutate(
        # tq_mutate args
        select     = adj_chl,
        mutate_fun = rollapply, 
        
        # rollapply args
        width      = 3,
        FUN        = mean,
        # mean args
        na.rm  = TRUE,
        # tq_mutate args
        col_rename = "mean_3"
    )   %>%
 ungroup()



max_chl <- chl_rollmean %>% group_by(TankNum) %>% 
  dplyr::select(TankNum,treatment,animal, disturb,mean_3, block) %>%
  filter(mean_3 == max(mean_3, na.rm = T))

max_chl$animal <- as.factor(max_chl$animal)
## Put the order of the factors in a more reasonable order
max_chl$animal <- factor(max_chl$animal, levels = c("none", "snail", "daphnia", "both"))
max_chl$disturb <- as.factor(max_chl$disturb)
max_chl$disturb <- factor(max_chl$disturb, levels = c("y","n"))
``` 

linear model
```{r}
maxmod <- lmer(log(mean_3) ~ -1+animal*disturb + (1|block), data = max_chl)
plot(resid(maxmod))
qqnorm(resid(maxmod))
```

contrasts of interest
```{r}


###compares differences of differences- checked with output of summany(maxmod)- gets correct mean estimates

mchl <- contrast(regrid(emmeans(maxmod, ~animal*disturb)), interaction = c("pairwise"), by = NULL)

summary(maxmod)

##for graphing
mchl1 <- emmeans(maxmod, ~animal*disturb)
mchl2 <- data.frame(confint(pairs(mchl1, simple = "disturb")))


```


Ammonium final day
```{r}

amm_final <- lmer(log(NH4)~animal*disturb + (1|block), data = finday)
plot(resid(amm_final))
qqnorm(resid(amm_final))
```

Contrasts
```{r}
ammfin <- contrast(regrid(emmeans(amm_final, ~animal*disturb)), interaction = c("pairwise"), by = NULL)

##for graphing
ammfin1 <- emmeans(amm_final, ~animal*disturb)
ammfin2 <- data.frame(confint(pairs(ammfin1, simple = "disturb")))
```

Ammonium maximum model
```{r}
## make column with max NH4 reached after day 19
dat_max <- dat %>% filter(ExptDay > 19) %>% group_by(TankNum) %>% mutate(max_nh4= max(NH4,na.rm = T)) %>% ungroup()
#filter for only days with highest ammonium reached
dat_max2 <- dat_max %>% group_by(TankNum) %>% filter(NH4==max_nh4)

amm_max <- lmer(log(NH4) ~ animal*disturb + (1|block), data = dat_max2)
plot(resid(amm_max))
qqnorm(resid(amm_max))

```
Contrasts
```{r}
mfin <- contrast(regrid(emmeans(amm_max, ~animal*disturb)),interaction = c("pairwise"), by = NULL)

##for graphing
mfin1 <- emmeans(amm_max, ~animal*disturb)
mfin2 <- data.frame(confint(pairs(mfin1, simple = "disturb")))

```
Graphing
```{r}
g <- ggplot(data = chlfin2, aes(exp(estimate), animal)) + geom_point(size=3) + geom_errorbarh(aes(xmin=exp(lower.CL), xmax = exp(upper.CL)), height = 0.3) + ylab("Herbivore Treatment") + xlab(str_wrap("Proportional Change in Final Chlorophyll (ug/L)", width = 25 )) + theme(axis.line = element_line(colour = "black"), panel.border = element_blank()) + ggtitle("A.") 

g1 <- ggplot(data = mchl2, aes(exp(estimate), animal)) + geom_point(size=3) + geom_errorbarh(aes(xmin=exp(lower.CL), xmax = exp(upper.CL)), height = 0.3) + ylab(" ") + xlab(str_wrap("Proportional Change in Maximum Chlorophyll (ug/L)", width = 27)) + theme(axis.line = element_line(colour = "black"), panel.border = element_blank()) + ggtitle("B.") 

g2 <- ggplot(data = ammfin2, aes(exp(estimate), animal)) + geom_point(size=3) + geom_errorbarh(aes(xmin=exp(lower.CL), xmax = exp(upper.CL)), height = 0.3) + ylab("Herbivore Treatment") + xlab(str_wrap("Proportional Change in Final Ammonium (mg/L)",width = 25)) + theme(axis.line = element_line(colour = "black"), panel.border = element_blank()) + ggtitle("C.") 

g3 <- ggplot(data = mfin2, aes(exp(estimate), animal)) + geom_point(size=3) + geom_errorbarh(aes(xmin=exp(lower.CL), xmax = exp(upper.CL)), height = 0.3) + ylab(" ") + xlab(str_wrap("Proportional Change in Maximum Ammonium (mg/L)", width = 25)) + theme(axis.line = element_line(colour = "black"), panel.border = element_blank()) + ggtitle("D.") 

grid.arrange(g,g1,g2,g3)

```

