---
title: "Group_project"
author: "Jo"
date: "October 28, 2019"
output: html_document
---

read in data add in treatment numbers
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("fix_chl.R")
source("Graphing_Set_Up.R")
library(lme4)
library(coefplot)
library(nlme)
```


Remove treatments with ceriodaphnia since they didn't survive
```{r}
dat <- newdat %>% filter(treatment != 5 & treatment != 6 & treatment != 9 & treatment != 10 & treatment != 13 & treatment != 14 )


```

make a columns for disturbed/undistrubed and both/none/cladoceran/snail

```{r}

dat$disturb <- "X"
  
for (i in 1:nrow(dat)){
  if (dat$treatment[i] ==2| dat$treatment[i] ==4| dat$treatment[i] ==8|
      dat$treatment[i] ==12){
    dat$disturb[i] <- "y"
  } else if (dat$treatment[i] ==1|dat$treatment[i] ==3|dat$treatment[i] ==7|dat$treatment[i] ==11){
    dat$disturb[i] <- "n"
  }}

dat$animal <- "X"

for (i in 1:nrow(dat)){
  if (dat$treatment[i] ==3| dat$treatment[i] ==4){
    dat$animal[i] <- "daphnia"
  } else if (dat$treatment[i] ==7|dat$treatment[i] ==8){
    dat$animal[i] <- "snail"
  } else if (dat$treatment[i] ==11|dat$treatment[i] ==12){
    dat$animal[i] <- "both"}
  else if (dat$treatment[i] ==1|dat$treatment[i] ==2){
    dat$animal[i] <- "none"}
}





```




Subset final time point for Nh4 and final 4 days for Chl
```{r final time point}
fday <- dat %>% filter(ExptDay == 40)
l <- as.numeric(unique(fday$TankNum))
fday1 <- dat %>% filter(ExptDay == 39) %>% filter(TankNum !=20 & TankNum !=21 & TankNum !=22 & TankNum != 23 &
                                                  TankNum !=24 & TankNum !=25 & TankNum !=26 & TankNum != 27 & 
                                                  TankNum !=28 & TankNum !=29 & TankNum !=30 & TankNum != 31 & 
                                                  TankNum !=32 & TankNum !=33 & TankNum !=34 & TankNum != 35 & 
                                                  TankNum !=36 & TankNum !=37 & TankNum !=38 & TankNum != 39 & 
                                                  TankNum !=40 & TankNum !=83 & TankNum !=84 & TankNum != 85 & 
                                                  TankNum !=86 & TankNum !=87 & TankNum !=88 & TankNum != 89 & 
                                                  TankNum !=90 & TankNum !=91 & TankNum !=92 & TankNum != 93 &
                                                  TankNum !=94 & TankNum !=95 & TankNum !=96 & TankNum != 97 & 
                                                  TankNum !=98 & TankNum !=99 & TankNum !=100& TankNum != 101 & 
                                                  TankNum != 102 & TankNum != 103 & TankNum != 104 & TankNum != 105 & 
                                                  TankNum != 106 & TankNum != 107) 
finday <- rbind(fday, fday1)



endday <- dat %>% filter(ExptDay == 40 | ExptDay == 39 | ExptDay == 38 | ExptDay == 37)
endday1 <- dat %>% filter(ExptDay == 36) %>% filter(TankNum !=20 & TankNum !=21 & TankNum !=22 & TankNum != 23 &
                                                  TankNum !=24 & TankNum !=25 & TankNum !=26 & TankNum != 27 & 
                                                  TankNum !=28 & TankNum !=29 & TankNum !=30 & TankNum != 31 & 
                                                  TankNum !=32 & TankNum !=33 & TankNum !=34 & TankNum != 35 & 
                                                  TankNum !=36 & TankNum !=37 & TankNum !=38 & TankNum != 39 & 
                                                  TankNum !=40 & TankNum !=83 & TankNum !=84 & TankNum != 85 & 
                                                  TankNum !=86 & TankNum !=87 & TankNum !=88 & TankNum != 89 & 
                                                  TankNum !=90 & TankNum !=91 & TankNum !=92 & TankNum != 93 &
                                                  TankNum !=94 & TankNum !=95 & TankNum !=96 & TankNum != 97 & 
                                                  TankNum !=98 & TankNum !=99 & TankNum !=100& TankNum != 101 & 
                                                  TankNum != 102 & TankNum != 103 & TankNum != 104 & TankNum != 105 & 
                                                  TankNum != 106 & TankNum != 107)

end <- rbind(endday, endday1)


ggplot(data = end, aes(as.factor(treatment), Chl)) + geom_boxplot()

ggplot(data=finday, aes(as.factor(treatment), NH4)) + geom_boxplot()
```


 
```{r algal resilience}

dat1 <- end %>% filter(disturb == "y")

#######
## MPK Contrast stuff
#######

## Put the order of the factors in a more reasonable order
dat1$animal <- factor(dat1$animal, levels = c("none", "snail", "daphnia", "both"))

## Ben's stuff that I had a little bit of a hard time following because I am a bit unclear about which matrix he made and his
 ## comment about transpose confused me a bit

cont <- matrix(nrow = 4, ncol = 4
  , data = c(
    1/4,  1/4,  1/4,  1/4   ## Avg over all treatments
  , 1  , -1/3, -1/3, -1/3   ## no animal vs avg of the rest of the animals
  , 0  ,    1,    -1,   0   ## difference between snails and daphnia
  , 0  ,  1/2,   1/2,  -1   ## synergistic effect of both animals vs avg of daph and snails.  
  )
  , byrow = TRUE)



dimnames(cont) <- list(
  levels(dat1$animal)
, c(": intercept", ": avg", ": s vs d", ": both")
)

### Fit the model with contrasts
finmod <- lm(log(Chl) ~ animal, data = dat1, contrasts = list(animal = cont[,-1]))


### Clearly did something...
coefplot(finmod)


plot(resid(finmod))
qqnorm(resid(finmod))
```


Max Chl - resistance

```{r}
max_chl <- dat %>% group_by(TankNum) %>% slice(which.max(Chl))

max_chl$up <- max_chl$ExptDay + 1
max_chl$down <- max_chl$ExptDay - 1



```




Algal resistance, compare slope over time after disturbance
```{r algal resistance}
mod_res <- lme(Chl ~ as.factor(treatment), correlation = corAR1(form = ~ExptDay), data = dat)

```

Graph algae
```{r graph algae, echo=FALSE}
s <- summary(mod2)
coef_dat <- s$coefficients
coef_dat2 <- data.frame(
  coefficients = row.names(coef_dat),
  estimate = coef_dat[,1],
  std_error = coef_dat[,2]
)
```

NH4 resilience, final time point
```{r algal resilience}

```


NH4 resistance, compare slope over time after disturbance
```{r algal resistance}

```

Graph NH4
```{r graph algae, echo=FALSE}

```

