---
title: "Group_project"
author: "Jo"
date: "October 28, 2019"
output: html_document
---

read in data add in treatment numbers
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("fix_chl.R")
source("Graphing_Set_Up.R")
library(lme4)
library(coefplot)
library(nlme)
library(tidyquant)
library(emmeans)
library(multcomp)
library(lmerTest)
```


Remove treatments with ceriodaphnia since they didn't survive
```{r}
dat <- newdat %>% filter(! treatment %in% c(5,6,9,10,13,14))
```

make a columns for disturbed/undisturbed and both/none/cladoceran/snail

```{r}
dat$disturb <- "X"
  
for (i in 1:nrow(dat)){
  if (dat$treatment[i] ==2| dat$treatment[i] ==4| dat$treatment[i] ==8|
      dat$treatment[i] ==12){
    dat$disturb[i] <- "y"
  } else if (dat$treatment[i] ==1|dat$treatment[i] ==3|dat$treatment[i] ==7|dat$treatment[i] ==11){
    dat$disturb[i] <- "n"
  }}

dat$animal <- "X"

for (i in 1:nrow(dat)){
  if (dat$treatment[i] ==3| dat$treatment[i] ==4){
    dat$animal[i] <- "daphnia"
  } else if (dat$treatment[i] ==7|dat$treatment[i] ==8){
    dat$animal[i] <- "snail"
  } else if (dat$treatment[i] ==11|dat$treatment[i] ==12){
    dat$animal[i] <- "both"}
  else if (dat$treatment[i] ==1|dat$treatment[i] ==2){
    dat$animal[i] <- "none"}
}





```




Subset final time point for Nh4 and final 4 days for Chl
```{r final time point}
fday <- dat %>% filter(ExptDay == 40)
l <- as.numeric(unique(fday$TankNum))
fday1 <- dat %>% filter(ExptDay == 39) %>% filter(TankNum !=20 & TankNum !=21 & TankNum !=22 & TankNum != 23 &
                                                  TankNum !=24 & TankNum !=25 & TankNum !=26 & TankNum != 27 & 
                                                  TankNum !=28 & TankNum !=29 & TankNum !=30 & TankNum != 31 & 
                                                  TankNum !=32 & TankNum !=33 & TankNum !=34 & TankNum != 35 & 
                                                  TankNum !=36 & TankNum !=37 & TankNum !=38 & TankNum != 39 & 
                                                  TankNum !=40 & TankNum !=83 & TankNum !=84 & TankNum != 85 & 
                                                  TankNum !=86 & TankNum !=87 & TankNum !=88 & TankNum != 89 & 
                                                  TankNum !=90 & TankNum !=91 & TankNum !=92 & TankNum != 93 &
                                                  TankNum !=94 & TankNum !=95 & TankNum !=96 & TankNum != 97 & 
                                                  TankNum !=98 & TankNum !=99 & TankNum !=100& TankNum != 101 & 
                                                  TankNum != 102 & TankNum != 103 & TankNum != 104 & TankNum != 105 & 
                                                  TankNum != 106 & TankNum != 107) 
finday <- rbind(fday, fday1)



endday <- dat %>% filter(ExptDay == 40 | ExptDay == 39 | ExptDay == 38 | ExptDay == 37)
endday1 <- dat %>% filter(ExptDay == 36) %>% filter(TankNum !=20 & TankNum !=21 & TankNum !=22 & TankNum != 23 &
                                                  TankNum !=24 & TankNum !=25 & TankNum !=26 & TankNum != 27 & 
                                                  TankNum !=28 & TankNum !=29 & TankNum !=30 & TankNum != 31 & 
                                                  TankNum !=32 & TankNum !=33 & TankNum !=34 & TankNum != 35 & 
                                                  TankNum !=36 & TankNum !=37 & TankNum !=38 & TankNum != 39 & 
                                                  TankNum !=40 & TankNum !=83 & TankNum !=84 & TankNum != 85 & 
                                                  TankNum !=86 & TankNum !=87 & TankNum !=88 & TankNum != 89 & 
                                                  TankNum !=90 & TankNum !=91 & TankNum !=92 & TankNum != 93 &
                                                  TankNum !=94 & TankNum !=95 & TankNum !=96 & TankNum != 97 & 
                                                  TankNum !=98 & TankNum !=99 & TankNum !=100& TankNum != 101 & 
                                                  TankNum != 102 & TankNum != 103 & TankNum != 104 & TankNum != 105 & 
                                                  TankNum != 106 & TankNum != 107)

end <- rbind(endday, endday1)

mean_nh4 <- finday %>% filter(treatment == 1) %>% summarize(avg = mean(NH4))
mean_chl <- finday %>% filter(treatment == 1) %>% summarize(avg = mean(Chl))
ggplot(data = end, aes(as.factor(treatment), Chl)) + geom_boxplot()
ggplot(data = end, aes(as.factor(treatment), Chl/mean_chl$avg)) + geom_boxplot()

ggplot(data=finday, aes(as.factor(treatment), NH4/mean_nh4$avg)) + geom_boxplot()
```


 
```{r chl final}

dat1 <- end %>% filter(disturb == "y")


## Put the order of the factors in a more reasonable order
dat1$animal <- factor(dat1$animal, levels = c("none", "snail", "daphnia", "both"))



inverse_cont <- matrix(nrow = 4, ncol = 4
  , data = c(
    1  ,  -1,      0,    0   ## snail vs none
  , 1  ,   0,     -1,    0   ## daphnia vs none
  , 0  ,    1,    -1,    0   ## difference between snails and daphnia
  , 0  ,  1/2,   1/2,   -1   ## synergistic effect of both animals vs avg of daph and snails.  
  )
  , byrow = TRUE)



dimnames(inverse_cont) <- list(

  c( ": snail",": daphnia", ": s vs d", ": both")
  ,   levels(dat1$animal)
)

## attempt to invert contrast matrix: doesn't work because we have
##  linearly dependent contrasts (sums of columns 1-3 == column 4)
#try(cont <- solve(inverse_cont))

## fit model with one parameter per treatment
##   1. throw away non-positive values
##   2. set to some small value e.g. thresh <- 0.002
##      Chl[Chl<thresh] <- 0.001
##   3. censoring? (AER::tobit())

## it is only 2 points that are less than 0 so dropping them seems reasonable-- and 2 NAs that need to 
## be checked with data sheets

dat1 <- dat1 %>% filter(!is.na(adj_chl))



## no adjustment for negative values
finmod0 <- lm(log10(adj_chl) ~ -1 + animal, data = dat1)
finmodsq <- lm(sqrt(adj_chl) ~ -1 + animal, data = dat1)

#drop negative values
finmod00 <- lm(log10(adj_chl) ~ -1 + animal, data = dat1[dat1$adj_chl > 0, ])
finmod00sq <- lm(sqrt(adj_chl) ~ -1 + animal, data = dat1[dat1$adj_chl > 0, ])

# set threshhold
dat1[dat1$adj_chl < 0.001,] <- 0.1
finmodth <- lm(log10(adj_chl) ~ -1 + animal, data = dat1)

## two options look identical

m1 <- multcomp::glht(finmod00,inverse_cont)
(s <- summary(m1))
plot(m1)
## broom::tidy(m1) ##  sucks, unfortunately
coef(finmod00)  ## compare to coefficients
e1 <-  emmeans(finmod00, ~animal, type = "response")

plot(e1)
## vignette("multcomp-examples",package="multcomp") ## p. 11

### Fit the model with contrasts
## (don't do this, we hadn't inverted the contrast matrix yet)
## finmod <- lm(log(Chl) ~ animal, data = dat1, contrasts = list(animal = cont[,-1]))


plot(resid(finmod00))
qqnorm(resid(finmod00))
qqline(resid(finmod00),col=2) ## left-skewed
hist(resid(finmod00),col="gray")
## ?? consider sqrt() rather than log-transform?

plot(resid(finmod00sq))
qqnorm(resid(finmod00sq))
qqline(resid(finmod00sq),col=2) ## still left skewed but  a little more even?? 
hist(resid(finmod00sq),col="gray")

```


Max Chl - 

```{r max chl}

## need dummy date variable for tq_mutate to work....



Date <- paste(dat$Month, dat$Day,dat$Year, sep = "-")


betterDates <- as.Date(Date,
  format = "%B-%d-%Y")

dates <- data.frame(Dates1 = Date,
                    Dates2 = betterDates)

p <- dates %>% filter(is.na(Dates2))
which(is.na(dates$Dates2))
dates[c(390,400,409,418,421,440),2] <- "2019-03-02"
dates[419,2] <- "2019-01-31"
dates[498,2] <- "2019-02-03"
dates[(which(is.na(dates$Dates2))), 2] <- "2019-03-01"

dat$Date <- dates$Dates2

dat <- dat %>% filter(!is.na(adj_chl))
dat_dist <- dat %>% filter(ExptDay >= ExptDay[which(dat$Disturbed=="y")]) ## only days after disturbance

chl_rollmean <- dat_dist %>% group_by(treatment) %>%
    tq_mutate(
        # tq_mutate args
        select     = adj_chl,
        mutate_fun = rollapply, 
        
        # rollapply args
        width      = 3,
        FUN        = mean,
        # mean args
        na.rm  = TRUE,
        # tq_mutate args
        col_rename = "mean_3"
    ) 


max_chl <- chl_rollmean %>% group_by(TankNum) %>% 
  dplyr::select(TankNum,treatment,animal, disturb,mean_3) %>%
  filter(mean_3 == max(mean_3, na.rm = T)) %>% filter(disturb == "y")

max_chl$animal <- as.factor(max_chl$animal)
## Put the order of the factors in a more reasonable order
max_chl$animal <- factor(max_chl$animal, levels = c("none", "snail", "daphnia", "both"))

maxmod <- lm(log(mean_3) ~ animal, data = max_chl)

plot(resid(maxmod)) ##hmm definitely seems like a pattern but there aren't that many points
plot.new()
qqnorm(resid(maxmod))
qqline(resid(maxmod),col=2) ## also left skewed but not terrible?
hist(resid(maxmod),col="gray")
mm <- multcomp::glht(maxmod,inverse_cont)
(ss <- summary(mm))
plot(mm)
## broom::tidy(m1) ##  sucks, unfortunately
coef(maxmod)  ## compare to coefficients
e2 <-  emmeans(maxmod, ~animal)

plot(e2)

```

```{r plot chl slope}
ggplot(dat_dist,
       aes(x=ExptDay,adj_chl,
           colour=animal,
           shape=disturb))+geom_point()+
  scale_y_log10() +
  facet_wrap(~disturb)+
  geom_smooth(method="gam",formula=y~s(x,k=10,bs="cs"),
              method.args=list(method="REML"))+
  geom_line(aes(group=TankNum),alpha=0.1)
```

Could do this with GAMs: https://rpubs.com/bbolker/ratgrowthcurves

Algal resistance, compare slope over time after disturbance
```{r algal slope}
dat_dist <- transform(dat_dist,ExptDay0 = ExptDay-min(ExptDay,na.rm=TRUE))

mod_res <- lmer(log10(adj_chl) ~ animal*ExptDay0 + (1|TankNum),
                data = dat_dist,
                subset=(disturb=="y" & ExptDay0<=5))
summary(mod_res)
plot(resid(mod_res))
qqnorm(resid(mod_res))
mod_res2 <- lmer(log10(adj_chl) ~ -1 + animal + animal:ExptDay0 +
                   (1|TankNum),  ## ExpDay0|TankNum ?
                data = dat_dist,
                subset=(disturb=="y" & ExptDay0<=5))

inv_cont2 <- rbind(
  cbind(inverse_cont,matrix(0,4,4)),
  cbind(matrix(0,4,4),inverse_cont)
)
dimnames(inv_cont2) <- list(paste(rep(c("int","slope"),each=4),
                                  rownames(inv_cont2)),
                            names(fixef(mod_res2)))

m2 <- multcomp::glht(mod_res2,inv_cont2)
summary(m2)
## need to double-check this
```

Graph algae
```{r graph algae, echo=FALSE}
s <- summary(mod2)
coef_dat <- s$coefficients
coef_dat2 <- data.frame(
  coefficients = row.names(coef_dat),
  estimate = coef_dat[,1],
  std_error = coef_dat[,2]
)
```

NH4 resilience, final time point
```{r ammonium final}
finday1 <- finday %>% filter(disturb == "y")
finday1$animal <- factor(finday1$animal,levels = c("none", "snail", "daphnia", "both")) 
amm_end <- lm(data = finday1, NH4 ~ animal)


amm1 <- multcomp::glht(amm_end,inverse_cont)
(samm <- summary(amm1))
plot(amm1)
e1_amm <-  emmeans(amm_end, ~animal)

plot(e1_amm)

```


max Nh4 post disturbance
```{r ammonium max}
nh_max <- dat %>% filter(disturb == "y") %>% filter(ExptDay >= ExptDay[which(dat$Disturbed=="y")])
nh_max1 <- nh_max %>% group_by(TankNum) %>% mutate(max_nh4= max(NH4,na.rm = T))
nh_max1$animal <- factor(nh_max1$animal, levels = c("none", "snail", "daphnia", "both"))

nh4_max_mod <- lm(max_nh4 ~ animal, data = nh_max1)

amm_max <- multcomp::glht(nh4_max_mod,inverse_cont)
(smax <- summary(amm_max))
plot(amm_max)
e1_max <-  emmeans(nh4_max_mod, ~animal)

plot(e1_max)

```


```{r sediment data}
sed <- read.csv("sediment.csv")
newdat1 <- newdat %>% dplyr::select(TankNum, treatment)
sed1 <- left_join(newdat1, sed)
sed2 <- sed1 %>% filter(! treatment %in% c(5,6,9,10,13,14))
dat2 <- dat %>% dplyr::select(treatment, disturb, animal, TankNum)
sed3 <- left_join(dat2,sed2)
sed3$animal <- factor(sed3$animal,levels = c("none", "snail", "daphnia", "both"))

ggplot(data = sed3, aes(as.factor(treatment), sediment)) + geom_boxplot()
```


```{r sediment model}

sedmod <- lm(sediment ~ animal,data = sed3, subset=(disturb=="y") ) ## hmm do all my models need random effect of tank??-- i only have 2 measurement per tank...so that doesn't seem doable but should i do something? 

plot(resid(sedmod))
qqnorm(resid(sedmod)) ## yeah not good
qqline(resid(sedmod),col=2) 
hist(resid(sedmod),col="gray")

sedmulti <- multcomp::glht(sedmod,inverse_cont)
(sed_summ <- summary(sedmulti))
plot(sedmulti)
e1_sed <-  emmeans(sedmod, ~animal)

plot(e1_sed)


```
egg casing
```{r daphnia egg cases}
egg <- read.csv("egg_case.csv")
names(egg) <- c("TankNum","eggs")
egg1 <- left_join(newdat1, egg)
egg2 <- egg1 %>% filter(! treatment %in% c(5,6,9,10,13,14))
egg3 <- left_join(dat2,egg2)
egg3$animal <- factor(egg3$animal,levels = c("none", "snail", "daphnia", "both"))

```

```{r egg case model}

eggmod <- glm(eggs ~ animal, family = "binomial", data = egg3, subset=(disturb=="y"))

```

daphnia populations
daphnia size ratios
